Analysis of the included studies

### 2023-06-16 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Styling: broke long lines into multiple lines, etc

knitr::kable(no_vax_modelled, caption = 'Number of studies per disease for which vaccination was not modelled', format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

@@

write.xlsx(vax_as_single_intervention_studies, file = '../citation_tables/vax_as_single_intervention_studies.xlsx')
```

@@

```{r}
individual_representation <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, individual_representation, sort = TRUE) %>% 
  pivot_wider(names_from = individual_representation, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('compartments', 'agents', 'individuals_representation_other')) %>% 
  adorn_pct_formatting(... = c('compartments', 'agents', 'individuals_representation_other')) %>% 
  adorn_ns(... = c('compartments', 'agents', 'individuals_representation_other'))

@@

knitr::kable(mod_structure_vs_sensitivity_analysis, 'Sensitivity analysis in relation to model structure', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))

@@

```{r eval=FALSE}
papers_with_code_available <- compact_data_with_citation_keys_no_fmd %>% 
    filter(simulation_code_available == 'yes') %>% 
    as.data.frame()

openxlsx::write.xlsx(papers_with_code_available, file = '../citation_tables/papers_with_code_available.xlsx')

>>>>

knitr::kable(no_vax_modelled, 
             caption = sprintf("%s %s", 
                               'Number of studies per disease for',
                               'which vaccination was not modelled'
                               ), 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

@@

writexl::write_xlsx(vax_as_single_intervention_studies, 
          path = file.path("citation_tables", 
                           "studies_modelling_vax_for_comparison.xlsx"
                           )
           )
```

@@

```{r}
individual_representation <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, individual_representation, sort = TRUE) %>% 
  pivot_wider(names_from = individual_representation, values_from = n) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('compartments', 'agents', 
                            'individuals_representation_other')
                    ) %>% 
  adorn_pct_formatting(... = c('compartments', 'agents', 
                               'individuals_representation_other')
                       ) %>% 
  adorn_ns(... = c('compartments', 'agents', 
                   'individuals_representation_other')
           )

@@

knitr::kable(mod_structure_vs_sensitivity_analysis, 
             caption = 'Sensitivity analysis in relation to model structure', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))

@@

```{r eval=FALSE}
papers_with_code_available <- compact_data_with_citation_keys_no_fmd %>% 
    filter(simulation_code_available == 'yes') %>% 
  select(title, author, publication_year, paper_doi, publication_type, journal)

writexl::write_xlsx(papers_with_code_available, 
                     path = file.path("citation_tables", 
                                      "papers_with_code_available.xlsx")
                    )
```
